Towards the Internet of Things: A Real-World Testbed

### 2013-06-18 doc/paper- towards the internet of things/paper v1.tex

Smart grid as being one of the most important applications of the internet of things makes use of different technologies such as Zigbee in the WSN \cite{ref1}.  \cite{ref2} discusses the need to introduce IPV6 within the wireless sensor networks and discusses the the existing approaches as well as the issues related to introducing IPV6 on top of Zigbee. Such issues are fragmentation, frame size, addressing, and security issues. This paper introduces a real testbed that includes the whole TCP/IP protocol provided by the BLIP project that takes into consideration most of those issues and implement the two-way communication as needed by smart grids and measures the performance of such a system. 

>>>>

Smart grid as being one of the most important applications of the internet of things makes use of different technologies such as Zigbee in the WSN \cite{ref1}.  \cite{ref2} discusses the need to introduce IPV6 within the wireless sensor networks and discusses the the existing approaches as well as the issues related to introducing IPV6 on top of Zigbee. Such issues are fragmentation, frame size, addressing, and security issues. This paper introduces a real testbed that includes the whole TCP/IP protocol provided by the BLIP project that takes into consideration most of those issues and implement the two-way communication as needed by smart grids and measures the performance of such a system. El Kouche also investigates on the widely used architectures and technologies and explains which architecture is the most suitable for a WSN within the internet of things \cite{ref3}. \cite{ref4} discusses the requirement of the IOT gateway as well as a proposed architecture for the system to be deployed in the gateway.
